{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-29 wacv_for_review.tex
Typos in Experiments Section Fixed

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{x_t}$, represents the
target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
coordinates of the target's centroid, $v_x$ and $v_y$ are the velocity
estimated along the $x$-axis and $y$-axis. The particle filter
predicts, using a constant velocity motion model, a target's next
state by generating a predefined number of particles. Then it uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
and $M$ denote the size of rows and columns of the confidence map.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed algorithm {\it E}nKCF and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos of 100 objects whereas
UAV123 dataset contains aerial footages of 123 objects.  We first test
the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
With this version, our goal is to have an object tracking algorithm
that ``efficiently'' runs on an embedded system, a drone, in ``high
speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
dataset is a good fit in evaluating the performance of the proposed
algorithm. In addition, in the UAV123 dataset, there are many
challenging, realistic scenes, e.g., abrupt scale/illumination
changes. Although we are primarily interested in developing an
algorithm for mobile, embedded robotic applications, it is also
important to compare the performance of the proposed algorithm with
those of the state-of-the-art in a nominal dataset. To this end, we
chose the OTB100 dataset that contains the videos recorded from smart
phones and typical cameras in perspective view. Also, we tested the
proposed algorithm on a temporally down-sampled version of the UAV123
dataset, called UAV123$\_$10fps dataset. What we would like to
evaluate using this modified dataset is how robust the proposed
algorithm is to the drastic motions of camera and targets. Finally, we
evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
features, on the UAV123 dataset to observe how much gain we can
achieve over the hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high and low
speed tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
CCOT trackers originally uses deep convolutional features, however,
for the sake of fair comparison, we employ fHoG and color-naming
features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
the results on the UAV123 dataset. The {\it E}nKCF outperformed other
high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
accuracy, but 10-20 times slower. The more recent trackers, ECO and
CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
running at 10-15 times slower speed.  For the scale adaptation, {\it
  E}nKCF did fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
and $30$ times faster. We believe that there can be two reasons why {\it E}nKCF
outperforms the DSST that updates the scale every frame searching over
33 scale ratios. (1) The DSST uses a 1-D scale filter whereas ours applies a 2-D scale
filter. This might reduce the spatial information learned in the scale filter. (2) The
DSST scale filter originally employs only fHoG features whereas ours combines
both fHoG and color-naming features.

>>>>

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates the target's scale
at every other $k$ frames. Although the strategy of updating every other 
$k$th frames will result in an optimal run-time performance, this may lead 
drifts at the later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_{t}}$, represents the
target's pixel coordinates and its velocity, $\mathbf{X_{t}} = \lbrace
x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
coordinates of the target's centroid, $v_x$ and $v_y$ are the velocities
estimated along the $x$-axis and $y$-axis. The particle filter
predicts, using a constant velocity motion model, the target's next
state by generating a predefined number of particles. Then it uses the
confidence maps of {\it E}nKCF as observation to update its state. The
particle weight is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
and $M$ denote the number of rows and columns of the confidence map.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed {\it E}nKCF tracker and
its variants on the object tracking benchmark
datasets. Particularly, we choose two publicly available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos of 100 objects whereas
UAV123 dataset contains aerial footages of 123 objects.  We first test
the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
With this version, our goal is to have an object tracking algorithm
that ``efficiently'' runs on an embedded system, a drone, in ``high
speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
dataset is a good fit in evaluating the performance of the proposed
algorithm. In addition, in the UAV123 dataset, there are many
challenging, realistic scenes, e.g., abrupt scale/illumination
changes. Although we are primarily interested in developing an
algorithm for mobile, embedded robotic applications, it is also
important to compare the performance of the proposed algorithm with
those of the state-of-the-art in a nominal dataset. To this end, we
chose the OTB100 dataset that contains the videos recorded from smart
phones and typical cameras in perspective view. Also, we tested the
proposed algorithm on a temporally down-sampled version of the UAV123
dataset, called UAV123$\_$10fps dataset. What we would like to
evaluate using this modified dataset is how robust the proposed
algorithm is to the drastic motions of camera and targets. Finally, we
evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
features, on the UAV123 dataset to observe how much gain we can
achieve over the hand-crafted features.

\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
       {\it E}nKCF is designed to address specific challenges in
       single target tracking problem, the optimal parameters for
       individual KCFs should be different. We set the learning rates
       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
       the Gaussian neighboring function, we empirically found the
       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
       ratio. The padding size for the correlation filters is tuned to
       $2$ for $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for
       $R_{s}$. For our particle filter implementation, we empirically
       set the number of particles to $1,000$ to balance the run-time
       performance and accuracy. To keep the level of variance among
       the particles reasonable, we performed the re-sampling only
       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
       pre-defined threshold.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art high-speed and low-speed trackers. 
For the precision, we rank the trackers based on the precision numbers 
at 20 pixels whereas in the success rate plots, trackers are ranked based 
on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
relatively lower-speed ($\leq$50): ECO \cite{DanelljanCVPR2017}, CCOT
\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
CCOT trackers originally uses deep convolutional features, however,
for the sake of fair comparison, we employ fHoG and color-naming
features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
the results on the UAV123 dataset. The {\it E}nKCF outperformed other
high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
accuracy, but 10-20 times slower. The more recent trackers, ECO and
CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
running at 10-15 times slower speed.  For the scale adaptation, {\it
  E}nKCF did fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
and $30$ times faster. We believe that there can be two reasons why {\it E}nKCF
outperforms the DSST that updates the scale every frame searching over
33 scale ratios. (1) The DSST uses a 1-D scale filter whereas ours applies a 2-D scale
filter. This might reduce the spatial information learned in the scale filter. (2) The
DSST scale filter originally employs only fHoG features whereas ours combines
both fHoG and color-naming features.
